---
title: "Task 1 Volodin Sergei"
output:
  html_document: default
  html_notebook: default
---

The algorithm:

1. Generate N samples
2. Run Student t-test and blah-blah-blah

Parameters

```{r}
n_range <- seq(5, 50, by = 5)
mu_range <- seq(0, 2, by = 0.1)
```

This function generates datasets, runs two criteria and outputs p-value.

```{r, eval = FALSE}
run_one_dataset <- function(n, mu)
{
  x1 <- rnorm(n, mean = 0, sd = 1)
  x2 <- x1 + rnorm(n, mean = mu, sd = 4)
  res <- c(0, 0)
  res[1] <- t.test(x1, x2, paired = TRUE)$p.value
  res[2] <- wilcox.test(x1, x2, paired = TRUE)$p.value
  res
}

```

This function generates N datasets and then outputs p_values and P(H1)

out: two-dimensional array
first index: p_values / P(H1)
second index: number of algorithm (Student/Wilcox)

```{r, eval = FALSE}
library(parallel)
cl <- makeCluster(4)
clusterExport(cl, "run_one_dataset")
```

```{r, eval = FALSE}
run_multiple_datasets <- function(N, n, mu)
{
  p_values = parSapply(cl, 1:N, function(x) {run_one_dataset(n, mu)})
  
  res = array(dim = c(2, 2))
  res[1,] <- rowMeans(p_values)
  res[2,] <- rowSums(p_values <= 0.05) / N
  res
}
```

```{r, eval = FALSE}
N <- 10000

# indices: n, mu, (pvalue/P(H1), (Student/Wilcox))
res <- array(dim = c(length(n_range), length(mu_range), 2, 2))
i <- 1
for(n in n_range)
{
  j <- 1
  for(mu in mu_range)
  {
    clusterExport(cl, c("n", "mu"))
    res[i,j,,] <- run_multiple_datasets(N, n, mu)
    j <- j + 1
  }
  i <- i + 1
}
```

```{r, eval = FALSE}
save(res, file = "res.RData")
```

```{r, eval = FALSE}
stopCluster(cl)
```

```{r}
load("res.RData")
```

Define plot function

```{r}
col_1 = "red"
col_2 = "blue"

plot_one <- function(x, y1, y2, xlab, ylab, title, sub = "")
{
  ylim = range(c(y1, y2))
  plot(x = x, y = y1, type="b", xlab = xlab, ylab = ylab, col=col_1, ylim = ylim, main = title, sub = sub)
  par(new = TRUE)
  plot(x = x, y = y2, type="b", col = col_2, ylab = "", xlab = "", ylim = ylim)
  legend("bottomright", fill = c(col_1, col_2), c("Student", "Wilcox"))
}
```

Plot alpha

```{r}
plot_one(n_range, res[,1,2,1], res[,1,2,2], "n", "P(H1|H0)", "Alpha(n)", "mu = 0")
```

Plot p-values

```{r}
i = 1
for(n in n_range)
{
  sub = sprintf("n = %d", n)
  plot_one(mu_range, res[i,,1,1], res[i,,1,2], "mu", "p-value", "p-value(mu)", sub)
  i <- i + 1
}
```
Plot power

```{r}
i = 1
for(n in n_range)
{
  sub = sprintf("n = %d", n)
  plot_one(mu_range[-1], res[i,-1,2,1], res[i,-1,2,2], "mu", "Power", "Power(mu)", sub)
  i <- i + 1
}
```